The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-10-03 borel-regularity.tex
Write up 2d integral argument for convolution result

% hideable draft text
\newif\ifshowdraft
\showdraftfalse
\ifshowdraft
\newenvironment{draft}{\color{SlateBlue}}{\color{black}}
\else
\NewEnviron{draft}{\iffalse\expandafter\BODY\fi}
\fi

@@

@@

@@

    \laplace_{\zeta,\alpha+\beta}[\phi\ast_{\zeta,\alpha+\beta}\psi]=\laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.

@@

\color{violet}
In the convolution integral, $a$ and $a'$ move so that $\zeta(a)$ runs from $\alpha+\beta$ to $\zeta$ while $\zeta(a')$ goes from $\zeta_{\alpha+\beta}$ to $0$.

>>>>

% hideable draft text
\newif\ifshowdraft
\showdrafttrue
\ifshowdraft
\newenvironment{draft}{\color{SlateBlue}}{\color{black}}
\else
\NewEnviron{draft}{\iffalse\expandafter\BODY\fi}
\fi

@@

\begin{equation*}

@@

\end{equation*}

@@

\begin{equation}\label{eqn:gen-laplace-convol}
\laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta,\alpha+\beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.

@@

\begin{draft}
The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,. \]
In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $\alpha+\beta$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta - (\alpha + \beta)$ to $0$.

The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_\mathcal{M} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$. Thus, on $\mathcal{N}$, we have the identity
\begin{align*}
d\zeta(a) + d\zeta(a') & = d\zeta \\
d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta \\
d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
\end{align*}
which we can substitute into the integral above to get
\begin{align*}
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_\mathcal{M} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
& = \int_\mathcal{M} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
\end{align*}
\begin{todo}Now we need to explain why the grid lines can be projected to $\mathcal{J}_{\zeta(a), \alpha}$ and $\mathcal{J}_{\zeta(a'), \beta}$. Something seems off here. The tip of the wedge $\mathcal{N}$ should be at $\zeta = \alpha + \beta$, since that's the beginning of the ray $\mathcal{J}_{\zeta, \alpha + \beta}$. At that point, though, according to our definitions, $\mathcal{S}(\zeta)$ should consist of the point $\zeta(a) = \alpha + \beta$, and $\mathcal{S}'(\zeta)$ should consist of the point $\zeta(a') = 0$.

In my drawings, I assumed that the tip of the wedge $\mathcal{N}$ would be at the point where $\zeta(a) = \alpha$, $\zeta(a') = \beta$, and $\zeta = \alpha + \beta$. Now I'm skeptical about that. Is that point even in $\mathcal{N}$? If so, what distinguishes it from all the other points on the line $\zeta(a) + \zeta(a') = \alpha + \beta$? Since $\alpha$ and $\beta$ can vary without changing the left-hand side of equation~\eqref{eqn:gen-laplace-convol}, we must need to make a choice somewhere\ldots

Maybe me actually need to change the statement? I think the argument might wrap up neatly if the convolution on the left-hand side were $\phi \ast_{\zeta_\alpha, \beta} \psi$ instead.
\end{todo}
\begin{align*}
\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_{?} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \int_{?} e^{z\zeta(a')}\,\psi(a')\,d\zeta(a')
\end{align*}
\end{draft}

\color{violet}
In the convolution integral, $a$ and $a'$ move so that $\zeta(a)$ runs from $\alpha+\beta$ to $\zeta$ while $\zeta(a')$ goes from $\zeta_{\alpha+\beta}$ to $0$.
